\mytitle

### 2016-10-08 pdocs/thesis/introduction.tex
pdocs/article
Aki's comments on article and in general

This work tries to invite structural engineers to take active part in development of more realistic physis engines.
Current computer systems provide enough computing performance and efficient algorithms so collision detection and 
rigid body dynamics can be handled in real time in most scenarios.
Soft body dynamics in which  object are deformable is in many cases still too complicated for real time applications.
Finite element method will probably replace other methods by providing general solution at some time but not in very near future.
In this work focus is on method where rigid bodies are connected by constraints.

@@

In this work all theories in area of structural analysis are quite old and e.g. 
\cite{timoshenko} is typical reference. Main focus is on elastic and 
linear plastic parts of stress-strain curve and elastic and plastic section modulus.

@@

Physics engines cannot used in serious structural analysis but using structural analysis in physics engines is not rare.  
E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.
Already \cite{cg1988} used quite similar principles as in this work to handle plasticity.

@@

Main requirements for software implementation can be summarized
\begin{itemize}
\item plastic deformation takes place if force or moment exceeds given limit
\item plastic deformation absorbs enegry
\item after predefined limit of displacement is exceeded constraint is deactivated 
\item results should be in same magnitude as theoretical and test results
\item solution can be integrated to existing dynamics engines
\item additional calculation time for each timestep may not exceed few milliseconds 
\end{itemize}

Few decades ago software engineering and structural analysis were highly coupled
and e.g. \cite{bathe} and \cite{cook} contain very detailed instructions on
computer implementation. Those books provided good baseline for many computer 
standalone programs created in \lut for for analysis of 
thin-walled structures \cite{agifap,fsm,vtb}.  
Getting and compiling complicated software packages is currently quite easy. 
Understanding and getting enough knowledge to extend them requires a fair amount of hard work.

@@

Target of this work is to find out suitable methods for handling of plasticity and verify them 
in commonly used physics engine \bullet. 
Handling of plasticity basically means that objects involved may absorb kinetic energy and break.

@@

Methods presented in this work can be used in gaming industry to provide objects that behave more realistically than currently without significant extra work. Efficient simulation algorithms can also help in saving energy. Saving even few wats or percent for single user makes big difference as gaming PCs are estimated to have consumed 75 TWh/year of electricity globally in 2012, \cite{gaming.energy}.

>>>>

This work tries to invite structural engineers to take active part in development of more realistic physis engines.
Current computer systems provide enough computing performance and efficient algorithms so collision detection and 
rigid body dynamics can be handled in real time in most scenarios.
Soft body dynamics in which  bodies are deformable is in many cases still too complicated for real time applications.
Finite element method will probably replace other methods by providing general solution at some time but not in near future.
In this work focus is on method where rigid bodies are connected by constraints.

@@

In this work all theories in area of structural analysis are old and e.g. 
\cite{timoshenko} is typical reference. Main focus is on elastic and 
linear plastic parts of stress-strain curve and elastic and plastic section modulus.

@@

Physics engines cannot used in serious structural analysis but using structural analysis in physics engines is not rare.  
E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.

Already \cite{cg1988} used similar principles as in this work to handle plasticity and there are a few further
papers that cite \cite{cg1988}. E.g. following papers provide alternative solutions to similar kind of simulations as 
are handled in this work 
\begin{itemize}
\item \cite{gibson1997survey} presents extensive study on deformable modelling in computer graphics
\item \cite{o2002graphical} provides excellent paper on ductile behaviour of material
\item \cite{muller2004point} presents a method for modeling and animating of 
elastic and plastic bodies in realtime using point based animation
\item \cite{irving2004invertible} introduces algortithm for  finite element simulation of elastoplastic solids with
large deformations in reasonable time 
\end{itemize}

@@

Main requirements for software implementation can be summarized
\begin{itemize}
\item plastic deformation takes place if force or moment exceeds given limit
\item plastic deformation absorbs energy
\item after predefined limit of displacement is exceeded constraint is deactivated 
\item results should be in same magnitude as theoretical and test results
\item solution can be integrated to existing dynamics engines
\item additional calculation time for each timestep may not exceed few milliseconds 
\end{itemize}

Few decades ago software engineering and structural analysis were highly coupled
and e.g. \cite{bathe} and \cite{cook} contain detailed instructions on
computer implementation. Those books provided good baseline for many computer 
standalone programs created in \lut for for analysis of 
thin-walled structures \cite{agifap,fsm,vtb}.  
Getting and compiling complicated software packages is currently easy. 
Understanding and getting enough knowledge to extend them requires a fair amount of hard work.

@@

Target of this work is to find out suitable methods for handling of plasticity and verify them 
in commonly used physics engine \bullet. 
Handling of plasticity basically means that involved bodies may absorb kinetic energy and break.

@@

Methods presented in this work can be used in gaming industry to provide 
bodies that behave more realistically than currently without significant extra work. 
Efficient simulation algorithms can also help in saving energy. 
Saving even few wats or percent for single user makes big difference as gaming PCs are estimated to have consumed 
75 TWh/year of electricity globally in 2012, \cite{gaming.energy}.
